Interfering with Noninterference \iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF and...?)}}\fi

### 2020-01-19 main.tex
a few notational quibbles

In particular, the observation $\obstrace(\seq{(\contour,\mach)})$ arising
from a contoured trace $\seq{(\contour,\mach)}$ is sequence of state
observations $\stateobs_0,\, \stateobs_1,\, \ldots$ defined informally as
follows:
\begin{itemize}
\item $\stateobs_0$ maps every visible component (where $\contour_0 = \VIS$)
to its value in $\mach_0$ and every hidden
component to $\bot$; 
\item $\stateobs_{i+1}$ is defined from $\stateobs_{i}$ by (1) for each
visible component (where $\contour_{i+1} = \VIS$), copying its
value from $\mach_{i+1}$, and (2) for each
hidden component, where $\contour_i = \VIS$, copying its
value from $\stateobs_{i+1}$, and (3) if the resulting $\stateobs_{i+1}$ is
identical to $\stateobs_{i}$, then skipping $\stateobs_{i+1}$.
\iftext\bcp{Too informal!!}\fi
\end{itemize}

@@

(Lockstep-)Noninterference is the contoured lockstep hyperproperty
where:
\begin{itemize}
\item For each pair of traces in the hyperproperty, all the contours
  coincide.
\item For each pair of traces in the hyperproperty, If the initial
  machine states plus contour are variants, then the observervations
  of the two traces coincide.
\end{itemize}

@@

  For every pair of traces $\overline{(C, M)}_n$ and $\overline{(C,
    M')}_n$ in the set, and for every $0 \leq i < n$, there exists in
  the set a pair of traces $\overline{(C', N)}_m$ and $\overline{(C',
    N')}_m$ such that $C_0' = C_i$, $N_0 = M_i$, and $N_0' = M_i'$.

@@

  For every pair of traces $\overline{(C, M)}_n$ and $\overline{(C,
    M')}_n$ in the set, and for every machine state $N_0$ such that
  $N_0$ is a variant of $M_0$, there exists in the set a pair of
  traces $\overline{(C, M)}_m$ and $\overline{(C, N)}_m$.

>>>>

In particular, the observation $\obstrace(\seq{(\contour,\mach)})$ arising
from a contoured trace $\seq{(\contour,\mach)}$ is sequence of state
observations $\stateobs_0,\, \stateobs_1,\, \ldots$ defined informally as
follows:
\begin{itemize}
\item $\stateobs_0$ maps every visible component (where $\contour_0 = \VIS$)
to its value in $\mach_0$ and every hidden
component to $\bot$; 
\item $\stateobs_{i+1}$ is defined from $\stateobs_{i}$ by (1) for each
visible component (where $\contour_{i+1} = \VIS$), copying its
value from $\mach_{i+1}$\apt{$\mach_i$ ?}, and (2) for each
hidden component, where $\contour_i = \VIS$, copying its
value from $\stateobs_{i+1}$, and (3) if the resulting $\stateobs_{i+1}$ is
identical to $\stateobs_{i}$, then skipping $\stateobs_{i+1}$.
\iftext\bcp{Too informal!!}\fi
\end{itemize}

@@

(Lockstep-)Noninterference is the contoured lockstep hyperproperty
where:
\begin{itemize}
\item For each pair of traces in the hyperproperty, all the contours
  coincide.\apt{This is still a bit ambiguous. How about: For each pair of
    contoured traces in the hyperproperty, the contour is invariant 
    along each trace.}
  \item For each pair of contoured traces in the hyperproperty, if the
    initial elements of the traces are variants, then the observervations
    of the two traces coincide.
\end{itemize}

@@

  For every pair of traces $\overline{(C, M)}_n$ and $\overline{(C,
    M')}_n$ in the set, and for every $0 \leq i < n$, there exists in
  the set a pair of traces $\overline{(C', N)}_m$ and $\overline{(C',
    N')}_m$ such that $C_0' = C_i$, $N_0 = M_i$, and $N_0' = M_i'$.
  \apt{I don't see how we can leave $m$ unspecified: doesn't it need to be as long as possible subject to well-formedness? Also, the evolution of $C$ is not determined by the machine, so don't we need $C_j' = C_{i+j}$ for all $0 \leq j < m$ ? }

@@

  For every pair of traces $\overline{(C, M)}_n$ and $\overline{(C,
    M')}_n$ in the set, and for every machine state $N_0$ such that
  $N_0$ is a variant of $M_0$, there exists in the set a pair of
  traces $\overline{(C, M)}_m$ and $\overline{(C, N)}_m$.\apt{Same complaint about $n$. And again, $N_0$ defines $\overline{N}$ but it doesn't define $\overline{(C,N)}$. }
